My Findings

### 2024-06-14 Findings (Shared Folder)/Chapters/randomNotes.tex
Updates from Overleaf

\subsubsection{Spiraling in to the Origin}
We can start with the vector field $ F(x,y) = (x,y) $ and this time, rather time rotating it with a rotation matrix, we can rotate that using a matrix corresponding to a complex number $ z = \mu + i \omega $, i.e.
\[ F_\text{new}(x,y) = \matt{\mu}{-\omega}{\omega}{\mu}F(x,y). \]
We can take this complex number to be $ z = -1 + i $. Thus our new vector field will be
\[ F_\text{new}(x,y) = (-x+y, -x-y).  \]
So our PDE will read
\[ \frac{\partial \rho}{\partial t} = \nabla^2 \rho + (-x+y)\frac{\partial \rho}{\partial x} + (-x-y)\frac{\partial \rho}{\partial y} - 2\rho. \]
Simulating this PDE we will get

>>>>

\subsubsection{Spiraling in to the Origin}
We can start with the vector field $ F(x,y) = (x,y) $ and this time, instead of rotating it with a rotation matrix, we can rotate that using a matrix corresponding to a complex number $ z = \mu + i \omega $, i.e.
\[ F_\text{new}(x,y) = \matt{\mu}{-\omega}{\omega}{\mu}F(x,y). \]
We can take this complex number to be $ z = -1 + i $. Thus our new vector field will be
\[ F_\text{new}(x,y) = (-x+y, -x-y).  \]
So our PDE will read
\[ \frac{\partial \rho}{\partial t} = \nabla^2 \rho + (-x+y)\frac{\partial \rho}{\partial x} + (-x-y)\frac{\partial \rho}{\partial y} - 2\rho. \]
Simulating this PDE we will get
